Stack Safety as a Security Property

### 2020-07-03 main.tex
wibbles, comments

To help keep things concrete throughout the more technical sections
that follow, we are first going to introduce a running example. We are
going to use it to demonstrate various potentially problematic
behaviours in this section, and then show how our properties and
enforcement mechanisms preclude them later on in the paper.

@@

@@

To show a trace of the execution of this program, we are going to need
a low-level view of both the code and the machine it runs on. While
our concrete implementation (Section~\leo{cite}) operates on a full
conventional RISC-V architecture, we will make a few simplifying
assumptions here to ease the exposition.

\bcp{We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack)}
First of all, we are going to ignore the heap. We are mainly concerned
with stack interactions so that will be the main focus. \leo{We're
  going to come back to that at the end. Will we?} We are then going
to abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated output at location 99, and lay the stack from
location 100 upwards. \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the memory layout at that point can be found in the top of
Figure~\ref{fig:running-trace-b}: instructions for {\tt main} begin at
0, the dedicated output is empty, while the (uninitialized) stack
begins at 100. Directly below the layout, we summarize the parts of
the register file that are relevant to the example.
%
The rest of Figure~\ref{fig:running-trace-b} details the execution of the
program, showing the machine state at call and return points, as well
as describing the full effect of each instruction in detail.
\leo{Expand upon this?}

>>>>

To help keep things concrete throughout the more technical sections
that follow, we first introduce a running example. We will
use it to demonstrate various potentially problematic
behaviours in this section, and then show how our properties and
enforcement mechanisms preclude them later on in the paper.

@@

        {Zero out result\apt{why?}}

@@

To show a trace of the execution of this program, we need
a low-level view of both the code and the machine it runs on. While
our concrete implementation (Section~\leo{cite}) operates on a full
conventional RISC-V architecture, we make a few simplifying
assumptions here to ease the exposition.

\bcp{We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack)}
First of all, we ignore the heap. We are mainly concerned
with stack interactions so that will be the main focus. \leo{We're
  going to come back to that at the end. Will we?} We also
abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated output at location 99, and lay the stack from
location 100 upwards. \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the memory layout at that point can be found in the top of
Figure~\ref{fig:running-trace-b}: instructions for {\tt main} begin at
0, the dedicated output is empty, while the (uninitialized) stack
begins at 100. Directly below the layout, we summarize the parts of
the register file that are relevant to the example.
%
The rest of Figure~\ref{fig:running-trace-b} details the execution of the
program, showing the machine state at call and return points, as well
as describing the full effect of each instruction in detail.
\leo{Expand upon this?}

\apt{Need to clarify to what extent our properties depend on the
particular compilation style, calling sequences, etc. illustrated here.}
